---
title: "Jeopardy"
output: html_notebook
---

load resources

```{r}
library(readr)
library(stringr)
library(dplyr)
library(tidyr)
```
Read the dataset into a tibble called jeopardy using tidyverse

```{r}
original <- read_csv("JEOPARDY_CSV.csv")
```
Print out the first 5 rows of jeopardy
Print out the columns of the jeopardy data
Replace the spaces with underscores for each column and
lowercase all of the column names


```{r}
head(original)
print(colnames(original))
colnames(original) <- str_replace_all(colnames(original), " ", "_")
colnames(original) <- tolower(colnames(original))
print(colnames(original))
typeof(original$show_number)
class(original$show_number)
typeof(original[,1])
class(original[,1])

class(original$value)
typeof(original$value)
```

remove the rows when the value column is "None"
remove the "$" and ",", then convert the value column to be numeric

```{r}
data <- original %>%
  filter(value != "None") 

#table(data$value)
#can't simply replace $ with ""
data <- data %>%
  mutate(value = str_replace_all(string = value, pattern = "[\\$\\,]", replacement = "")) %>% 
  mutate(value = as.numeric(value))

#class(data$value)

```
normalize the question, answer, and category columns

Lowercase all of the words of every question and answer

Remove all punctuation. Keep all letters and numbers.What about spaces?

```{r}
data <- data %>%
  mutate(category = tolower(category), question = tolower(question), answer = tolower(answer)) %>%
  mutate(category = str_replace_all(category,"[^a-z0-9\\s]",""), question = str_replace_all(question,"[^a-z0-9\\s]",""), answer = str_replace_all(answer,"[^a-z0-9\\s]",""))
```

Take the air_date column and split it into 3 new columns: year, month and day.
the separate() function can serve you well here
Convert each of these new columns into numeric columns as well
```{r}
data <- data %>%
  separate(air_date, c("year","month","day"), "-") 

data <- data %>%
  mutate(year = as.numeric(year), month = as.numeric(month), day = as.numeric(day))
```
For each of the three categories we discussed (science, history, Shakespeare), conduct a hypothesis test to see if they are more likely to appear than other categories. YES
```{r}

science <- 0
science_non <- 0
for (category in data$category) {
  if (str_detect(category,"science")) {
    science <- science + 1
  }
  else {
    science_non <- science_non + 1
  }
}

n_questions <- nrow(data)
p_category_expected <-   1/3369 
p_not_category_expected <- 3368/3369 
p_expected <- c(p_category_expected, p_not_category_expected)
p_observed <- c(science/n_questions, science_non/n_questions)
chisq.test(p_observed, p = p_expected, simulate.p.value = TRUE) #significant!
#the manual way
#chisq = (p_observed[1] - p_expected[1])**2/p_expected[1] + (p_observed[2] - p_expected[2])**2/p_expected[2]

history <- 0
history_non <- 0
for (category in data$category) {
  if (str_detect(category,"history")) {
    history <- history + 1
  }
  else {
    history_non <- history_non + 1
  }
}

n_questions <- nrow(data)
p_category_expected <-   1/3369 
p_not_category_expected <- 3368/3369 
p_expected <- c(p_category_expected, p_not_category_expected)
p_observed <- c(history/n_questions, history_non/n_questions)
chisq.test(p_observed, p = p_expected, simulate.p.value = TRUE) #significant!

shakespeare <- 0
shakespeare_non <- 0
for (category in data$category) {
  if (str_detect(category,"shakespeare")) {
    shakespeare <- shakespeare + 1
  }
  else {
    shakespeare_non <- shakespeare_non + 1
  }
}

n_questions <- nrow(data)
p_category_expected <-   1/3369 
p_not_category_expected <- 3368/3369 
p_expected <- c(p_category_expected, p_not_category_expected)
p_observed <- c(shakespeare/n_questions, shakespeare_non/n_questions)
chisq.test(p_observed, p = p_expected, simulate.p.value = TRUE) #significant!

```

how often new questions are repeats of older ones?

1. sort by accending air_date
2. Intialize an empty vector to store all the unique terms that are in the Jeopardy questions.
3. For each row, split the value for question into distinct words words, remove any word shorter than 6 characters, and check if each word occurs in terms_used
```{r}
data %>%
  arrange(year, month, day)
terms_used <- ""
for (i in c(1:nrow(data))) {
  if (i %% 10000 ==0) {print(i)}
  question <- data$question[i]
  words <- str_split(question," ", simplify = TRUE)
  for (word in words) {
    if (nchar(word) >=6 & !word %in% terms_used) {
            terms_used <- c(terms_used, word) 
    } 
  }
}
```
Find the value associated with each term
```{r}
for (term in terms_used) {
  for (question in data$question) {
    if (term %in% question) {
      ifelse()
    }
  }
}
```

